\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2019-11-29 submission/manuscript.Rmd
Optimized taxonomy plot.

```{r out.width="100%", fig.align="center", fig.cap="Bacteril Community\\label{community}", fig.pos="h"}
include_graphics("../results/figures/community_barplot.jpg")
```

>>>>

```{r out.width="100%", fig.align="center", fig.cap="Taxonomic classification and relative contribution of the most abundant bacterial sequences on the surfaces of two marine macrophytes (\\textit{Cymodocea nodosa} and \\textit{Caulerpa cylindracea}) from two locations (Saline and Funtana) and in two contrasting seasons (4 December 2017 and 19 June 2018).\\label{community}", fig.pos="h"}
include_graphics("../results/figures/community_barplot.jpg")
```

### 2019-11-29 submission/manuscript.tex
Optimized taxonomy plot.

\caption{Bacteril Community\label{community}}\label{fig:unnamed-chunk-2}
\end{figure}

>>>>

\caption{Taxonomic classification and relative contribution of the most abundant bacterial sequences on the surfaces of two marine macrophytes (\textit{Cymodocea nodosa} and \textit{Caulerpa cylindracea}) from two locations (Saline and Funtana) and in two contrasting seasons (4 December 2017 and 19 June 2018).\label{community}}\label{fig:unnamed-chunk-2}
\end{figure}
